---
title: "NYCFlights: Arrival Delay Regression Model"
author: "Shaofeng Deng"
date: "October 18, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(magrittr)
library(ggplot2)
library(psych)
```

# NYCFlights Model

Using the rectangular data that you created last week and following the *Predicting Medical Expenses* example from the text (*MLwR*), create a model for arr_delay. Follow MLwR structure 
for building a model. Describe/Explain each of the steps and show all work in codeblocks below.


## Step 1: Collect Data 

```{r "Step 1: Collect Data" }
YX <- read.csv("YX.csv",stringsAsFactors = T)
# Remove all observation with missing values
YX <- YX[complete.cases(YX),]
# Remove varibles with only one value or level
YX <- Filter(function(x)(length(unique(x))>1), YX)
```

## Step 2: Explore and Prep The Data


One of the things not done in the MLwR text is a pairwise comparison between the response and each of the predictors. Make sure to do this; this is often very illustrative of the relationship between that predictor and the response. This can be done with `pairs` or `psych::panel.pairs`


```{r "Step 2: Explore and Prep The Data" }
# Confirm the format of the data
str(YX)
# Summary of the responce
YX$arr_delay %>% summary
# Histogram of the responce
hist(YX$arr_delay)
# Corrolations between dependent varible and other varibles
nums <- sapply(YX, is.numeric)
co <- YX[nums] %>% cor(use="complete.obs")
co["arr_delay",]
# Use the most corrolated varibles to compute scatterplot matrix
psych::pairs.panels(YX[c("arr_delay", "dep_delay", "dep_time", "arr_time")])
```

## Step 3:  Train The Model

```{r "Step 3: Train The Model" }
# Use the most corrolated varibles as independent varibles to build a linear regression model
YX_model <- lm(arr_delay ~ dep_delay+dep_time+arr_time+air_time, data = YX)
YX_model

```

## Step 4: Evaluate Performance

Evaluating performance is a crutial step, that has yet to be treated well by the MLwR. Think about some of the tools that you have for evaluating performance.  Choose one and articulate why you have chosen it.

```{r "Step 4: Evaluate Performance" }
summary(YX_model)
# The multiple R-squared value of this model is pretty high, which shows that it explains nearly 80% of the dependent varible. Although the size of the errors and p-values are a bit concerning.
```


## Step 5: Improve Performance 

Show some steps for improving model performance.

```{r "Step 5: Improve Performance" }
YX$air_time2 <- YX$air_time^2
YX_model2 <- lm(arr_delay ~ dep_delay+dep_time*arr_time+air_time+air_time2, data = YX)
summary(YX_model2)
# Here we add a nonlinear trem for air_time and add interaction between dep_time and arr_time as they are supposed to. The result is a slight improve in the performence but not much.
```


# Question:

Is this a good model?  (Write your answer here.)
The model does explain something pretty well. For example, it captures the fact that arrival delay is in proportion to departure delay. But in general, it's still an over-simplified model. First we abandon most of the varibles and only pick 4 of them. And the result shows that early departure flights tend to have small delay while early arrival flights tend to have large delay, which is weird.
