---
title: "NYCFlights: Arrival Delay Logictic Model"
author: "Shaofeng Deng"
date: "October 25, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(MASS)
library(readr)
library(lubridate)
library(magrittr)
library(lubridate)
library(stringr)
library(dplyr)
library(data.table)
```


## Logsitic and Inverse Logistic Transformation 

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.

- Plot the logistic function from  `[-10,10]`

- Write a R function for the inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

- Plot the Inverse Logistic function from `[0,1]`


**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`

```{r "Logistic and Inverse Logistic" }
l <- function(x){1/(1+exp(-x))}
ggplot(data.frame(x = c(-5, 5)), aes(x)) + stat_function(fun = l)
inv <- function(y){-log(1/y-1)}
ggplot(data.frame(x = c(0, 1)), aes(x)) + stat_function(fun = inv)
```


# NYCFlights Model

Using the rectangular data that you created from assignment and following the *Predicting Medical Expenses* example from the text (*MLwR*), create a model for arr_delay >= 15 minutes. Follow *MLwR* structure   for building a model. Describe/Explain each of the steps and show all work in codeblocks below.

KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file.   

## Step 1: Collect Data 

```{r "Step 1: Collect Data" }
yx <- read_csv("yx.csv")
yx <- yx[-1]
```

## Step 2: Explore and Prep The Data


One of the things not done in the MLwR text is a pairwise comparison between the response and each of the predictors. Make sure to do this; this is often very illustrative of the relationship between that predictor and the response. This can be done with `pairs` or `psych::panel.pairs`

## Response;

- arr_delay : right skewed, some negative 

- Hypothesis: flight delays are a function of weather, mechanical problems and 
  other factors:

## Predictors

This is reasonable list of variables that can be used 

- fligths
  - month             **
  - dep_delay (?)     ***
  - carrier / flight  *
  - origin            
  - dest 
  - air_time          **
  - distance          **  (can make up time in the air)
  - air time / hour / minute not known at end of flight
  
- planes
  - year              ** 
  - type              **
  - manufacture
  - engines          (not much variation)
  - seats
  - engine           **
  - speed  (not well populated)

- weather 
  - temp             
  - dewp
  - wind_dir         **+
  - wind_gust        **+ 
  - precip           **
  - pressure         **
  - visib            **
  
- airports (origin and dest)
  - faa or name
  - lat             ** dest(only)
  - lon             ** dest(only)
  - alt              
  
## Remark
This step is the same as in the last homework. Here we only prepare the data.
```{r "Step 2: Explore and Prep The Data" }
 y <- "arr_delay"
 xs <- c(
    'month','dep_delay','carrier','air_time','distance'
   ,'type','engine'
   ,'wind_dir','wind_speed','wind_gust','precip','pressure','visib'
   ,'lat.x','lon.x','lat.y','lon.y'
 )

 yx <- yx[ , c(y,xs)]
 
 # Remove Outliers

 yx <- yx[ yx$arr_delay >= quantile(yx$arr_delay,0.01,na.rm=TRUE) &  
           yx$arr_delay <= quantile(yx$arr_delay,0.96,na.rm=TRUE), ]
 
 # HANDLE NA VALUES
 yx <- yx[complete.cases(yx),]
 
 # Change arr_delay to logical
 yx$arr_delay <- yx$arr_delay >= 15
```

## Step 3:  Train The Model
Our naive guess is: `r yx$arr_delay  %>% l %>% mean()` 

Our naive rmse is: `r mean((yx[["arr_delay"]] %>% l)-(yx[["arr_delay"]] %>% l %>% mean) %>% .^2)  %>% sqrt`
```{r "Step 3: Train The Model" }
model <- glm(arr_delay ~.,family=binomial(link='logit'),data=yx %>% sample_n(1e5))
model
```

## Step 4: Evaluate Performance

Think about some of the tools that you have for evaluating performance.  Choose one and articulate why you have chosen it.

```{r "Step 4: Evaluate Performance" }
anova(model, test="Chisq")
```
The difference between the null deviance and the residual deviance shows how our model is doing against the null model (a model with only the intercept). The wider this gap, the better. Analyzing the table we can see the drop in deviance when adding each variable one at a time. Most of the varibles seem to significantly reduce the residual deviance.

## I can only get this far in 2 hours
## Step 5: Improve Performance  

Show some steps for improving model performance.

```{r "Step 5: Improve Performance" }

```


# Question:

Is this a good model?  (Write your answer here.)


# PART B:

Your model should be good at explaining tardiness. Now, assume that your job is to predict arrival delays a month in advance. You can no longer use all the features in your model. Retrain your model using only features that will be *known* only a month in advance of the departure time.  Show all steps as above.

